### 2025-11-10 Proposals/2025-NSF-EntropicGeometry/ProjectSummary.tex
Change Project Summary based on feedback from Alejandro; add Physics and Math affiliations to header

\noindent
\textbf{Intellectual Merit:}  \\
While the state spaces of classical mechanics and quantum mechanics have different structures, symplectic manifolds and projective spaces of complex Hilbert spaces, respectively, the spaces of classical and quantum \emph{statistical ensembles} have common features.  They are both convex subsets of a locally convex topological vector space whose metric is induced by the information entropy, or more specifically, by the Jensen-Shannon divergence.  Moreover, classical and quantum information theory have numerous corresponding features.  The primary advancement of the research will be to take those common and corresponding features and generalize them, providing a common, mathematically rigorous, foundational structure to both classical and quantum theories.  Such a generalization will provide further insight into the relationships among established physical theories and place constraints on the allowed mathematical structures in potential future physical theories. All axioms will be physically motivated and stated as properties of ensemble spaces.  Preliminary work shows that the symplectic form of classical mechanics and the inner product (i.e.~Born rule) of quantum mechanics can be recovered by the entropy, tightly linking the geometric and entropic structures, and that the states defined by mechanics can be understood as special cases of ensembles with the lowest possible entropy or the extreme points of the convex set.

>>>>

\noindent
\textbf{Intellectual Merit:}  \\
While the state spaces of classical mechanics and quantum mechanics have different structures, symplectic manifolds and projective spaces of complex Hilbert spaces, respectively, the spaces of classical and quantum \emph{statistical ensembles} have common features.  They are both convex subsets of a locally convex topological vector space whose metric is induced by the information entropy, or more specifically, by the Jensen-Shannon divergence.  Moreover, classical and quantum information theory have numerous corresponding features.  The primary advancement of the research will be to take those common and corresponding features and generalize them, providing a common, mathematically rigorous, foundational structure to both classical and quantum theories.  Such a generalization will provide further insight into the relationships among established physical theories and place constraints on the allowed mathematical structures in potential future physical theories. All axioms will be physically motivated and stated as properties of ensemble spaces.  Preliminary work indicates that the symplectic form of classical mechanics and the inner product (i.e.~Born rule) of quantum mechanics can be recovered by the entropy, tightly linking the geometric and entropic structures, and that the states defined by mechanics can be understood as special cases of ensembles with the lowest possible entropy or the extreme points of the convex set.
